Parsing Postfix log files

### 2007-10-22 doc/logparser.tex
Made the flow chart into a figure, which resulted in minor tidying. Small cleanups for overfull hboxes etc.

\newpage
\tableofcontents

@@

This flow chart shows the paths the data representing a mail/connection can
take through the parser algorithm.  The flow chart covers the most common
paths only; there are additional, uncommon paths which are excluded for the
sake of clarity.

\includegraphics{build/logparser-flow-chart.ps}

@@

    \item The appropriate action to take --- this is discussed in
        section~\refwithpage{mails-covered}.

@@

    \item [Log Mail Analyser] Please see the previous discussion in
        section~\refwithpage{prior art}.

>>>>

\newpage
\tableofcontents
\listoffigures

@@

Figure~\ref{flow chart image} shows the paths the data representing a
mail/connection can take through the parser algorithm.  The flow chart
covers the most common paths only; there are additional, uncommon paths
which are excluded for the sake of clarity, but are described in
section~\refwithpage{additional complications}.

% This is very likely to move around as the flow chart is as big as
% possible, so if any preceding text changes the flow chart may end up on
% the next page, which may not be a bad thing, maybe.  What woould be a bad
% thing is the \clearpage seems to cause a blank page sometimes, if the
% image is just slightly too big.
\showgraph{build/logparser-flow-chart.ps}{Parser flow chart}{flow chart
image}
\clearpage

@@

    \item The appropriate action to take --- discussed in
        section~\refwithpage{mails-covered}.

@@

    \item [Log Mail Analyser] Please see the previous in-depth discussion
        of Log Mail Analyser in section~\refwithpage{prior art}.
